Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-11 WSSSPE1_report/WSSSPE1_summary_report.tex
Make sure a name does not split into two lines.

\author{Daniel S. Katz$^{(1)}$, Hilmar Lapp$^{(2)}$, Ketan Maheshwari$^{(3)}$, Frank L\"{o}ffler$^{(4)}$, Matthew Turk$^{(5)}$, Marcus D. Hanwell$^{(6)}$, Nancy Wilkins-Diehr$^{(7)}$, James Hetherington$^{(8)}$, James Howison$^{(9)}$, Sou-Cheng T. Choi$^{(10)}$, Shel Swenson$^{(11)}$,  Bruce Berriman$^{(12)}$, Andy R. Terrel$^{(13)}$, Colin Venters$^{(14)}$}
\note{Authors, please add/check middle initials and affiliations.}

>>>>

\author{Daniel~S.~Katz$^{(1)}$, Hilmar~Lapp$^{(2)}$, Ketan~Maheshwari$^{(3)}$, Frank~L\"{o}ffler$^{(4)}$, 
Matthew~Turk$^{(5)}$, Marcus~D.~Hanwell$^{(6)}$, Nancy~Wilkins-Diehr$^{(7)}$, James~Hetherington$^{(8)}$, 
James~Howison$^{(9)}$, Sou-Cheng~T.~Choi$^{(10)}$, Shel~Swenson$^{(11)}$,  Bruce~Berriman$^{(12)}$, Andy~R.~Terrel$^{(13)}$, Colin~Venters$^{(14)}$}
\note{Authors, please add/check middle initials and affiliations.}
